\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-05-05 paper.tex
added zero and result v parsers

@@

    \begin{tcolorbox}
      \begin{lstlisting}[language=Haskell]
      oneItem         :: Parse Char
      oneItem []       = []
      oneItem (l : ls) = [(l, ls)]
     \end{lstlisting}
    \end{tcolorbox}

@@

      \begin{lstlisting}[language=Haskell]
      oneItem ""       = []
      oneItem "parser" = [('p', "arser")]
     \end{lstlisting}

>>>>

    For simplicity, the focus will remain on parsers that either fail and return an empty list of results, or succeed and return a singleton list.

@@

    \begin{lstlisting}[language=Haskell]
      oneItem         :: Parse Char
      oneItem []       = []
      oneItem (l : ls) = [(l, ls)]
    \end{lstlisting}

@@

    \begin{lstlisting}[language=Haskell]
      oneItem ""       = []
      oneItem "parser" = [('p', "arser")]
    \end{lstlisting}
    Secondly, the parser \textbf{zero} will always fail, regardless of the input string provided.

    \begin{lstlisting}[language=Haskell]
      zero :: Parse p
      zero = \input -> [] 
    \end{lstlisting}

    In other words, the outcome of the \textbf{zero} parser will always be an empty list. \\ \\
    Finally, the \textbf{result v} parser will always succeed by returning the value \textit{v} without consuming any input.

    \begin{lstlisting}[language=Haskell]
      result :: p -> Parse p
      result v input = [(v, input)]
    \end{lstlisting}
